Implications of afforestation policies for global markets

### 2024-02-24 paper.Rmd

Establishing a connection between the standard GTAP model and the GTM model was a two-step process. First, we identified the set of common variables that are included in both models and their closures. That is, we selected which variables would be determined endogenously by one model and held as exogenous in the other model. In our case, we modeled the return on land using the GTAP model and fed those results into the GTM model as exogenous. Then, the amount of land available for crop and livestock production was endogenously determined by the GTM model and fed into the GTAP model as an exogenous input. In the second step, we established the connection between the models on the software level. This step required that the GTAP model, which is written in GEMPACK, be able to handle with the inputs from the GTM model, which is written in GAMS, and submit the outputs back to the GTM model. As GEMPACK and GAMS were developed long before software integration became important or even possible, we had to create a set of user functions in R that executed both models, collected their outputs, and an created parameter files automatically.

With R being able to operate both the GTAP and GTM models automatically, we are able to formulate the combined solution of the both models as a fairly simple math program that is solved in R:

@@

where $V_1$ is a vector of all variables in both systems, i.e., all variables in GTAP and all variables in GTM, that is solved by the GTAP model (represented by function \mbox{GTAP}) into a vector of variables $V_2$. At the same time, when $V_2$ in processed by the GTM, its solution is $V_1$. To solve the system simultaneously, we require that $V_1$ and $V_2$ be equal. In our case, the vector of variables $V_1$ includes all GTAP variables and the land change variables, which are exogenous to the GTAP model; the output vector of variables $V_2$ contains the change in the rents, which is treated as exogenous in the GTM model. With several iterations, the system converges to the land change and land rent change that is consistent across the models, i.e., the land change results in the land rent changes that, when entered into the GTM model, result in the same land changes as assumed by the GTAP model.

>>>>

Establishing a connection between the standard GTAP model and the GTM model was a two-step process. First, we identified the set of common variables that are included in both models and their closures. That is, we selected which variables would be determined endogenously by one model and held as exogenous in the other model. In our case, we modeled the return on land using the GTAP model and fed those results into the GTM model as exogenous. Then, the amount of land available for crop and livestock production was endogenously determined by the GTM model and fed into the GTAP model as an exogenous input. In the second step, we established the connection between the models on the software level. This step required that the GTAP model, which is written in GEMPACK, be able to handle with the inputs from the GTM model, which is written in GAMS, and submit the outputs back to the GTM model. As GEMPACK and GAMS were developed long before software integration became important or even possible, we had to create a set of user functions in R that executed both models, collected their outputs, and created parameter files automatically.

Once R was able to operate both models automatically, we were then able to formulate the combined solution as a fairly simple math program that is solved in R:

@@

where $V_1$ is a vector of all the variables in both systems, i.e., all variables in GTAP and all variables in GTM. Of import, $V_1$ includes the land change variables, which are exogenous to the GTAP model. $V_1$ is then used by the GTAP model (represented by function \mbox{GTAP}) and its outputs are passed to GTM as a vector of variables $V_2$. This output vector contains the change in rents, which is treated as exogenous in the GTM model. GTM then processes the $V_2$ variables as inputs and passes its solution back to GTAP as $V_1$. To solve the system simultaneously, we require that $V_1$ and $V_2$ be equal. With several iterations, the system converges to the change in land and land rent that is consistent across the models, i.e., the land change results in the land rent changes that, when entered into the GTM model, result in the same land changes as assumed by the GTAP model.
